Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-21 ms.qmd
Figured out why border wasn't drawn. You need to have shape = 21 (a fillable shape). I didn't realise there were different types!

####################
# lnRR CV
####################
 dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
                      title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3),
                      y = rep(-1.1, 3))
y_adj = -3
# Terrestrial
  p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[3]) + 
  scale_fill_manual(values = "black")+ labs(title = dat_text$title[3]) +
  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)

# Marine
p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[2]) + 
  scale_fill_manual(values = "black") + labs(title = dat_text$title[2]) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

# Freshwater
p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
  scale_fill_manual(values = "black") + labs(title = dat_text$title[1]) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

@@

# Freshwater
  yadj2 = -6
  x_f = 0.6
  p_f_cv <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), colour = col[1]) + 
    scale_fill_manual(values = "black") + 
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

# Marine
  x_m = -0.4
  p_m_cv <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
                 colour = col[2]) + 
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

@@

x_t = 0
p_t_cv <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
               colour = col[3]) + 
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
  ylim(-6, 3.5)

>>>>

####################
# lnRR CV
####################
 dat_text <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
                      title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3),
                      y = rep(-1.1, 3))
y_adj = -3
# Terrestrial
  p_t_rr <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)

# Marine
p_m_rr <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

# Freshwater
p_f_rr <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

@@

# Freshwater
  yadj2 = -6
  x_f = 0.6
  p_f_cv <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

# Marine
  x_m = -0.4
  p_m_cv <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g =FALSE, k = FALSE) + 
    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

@@

x_t = 0
p_t_cv <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = FALSE, k = FALSE) + 
  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
  ylim(-6, 3.5)
